### 2016-12-23 docs/binary.tex

A second distribution function is introduced, denoted $g_i(\mathbf{r};t)$,
which describes the composition. The moments of this distribution, by
analogy with the hydrodynamic case with distribution
$f_i(\mathbf{r};t)$ given in
Eq.~\ref{lb-f-moments}, are written
\begin{equation}
\phi(\mathbf{r};t) = \sum_i g_i (\mathbf{r};t), \quad
j_\alpha(\mathbf{r};t) = \sum_i g_i(\mathbf{r};t) c_{i\alpha}, \quad
\Phi_{\alpha\beta}(\mathbf{r};t) = \sum_i g_i(\mathbf{r};t)
c_{i\alpha}c_{i\beta}.
\end{equation}
Again, the summation is over index $i$ which counts the number of
discrete velocity components for the relevant lattice Boltzmann
model $N_{\mathrm{vel}}$. However, for the Cahn-Hilliard equation,
the only relevant physical moments are the order parameter
$\phi(\mathbf{r};t)$ and the flux $j_\alpha(\mathbf{r};t)$, so
the quantity $\Phi_{\alpha\beta}(\mathbf{r};t)$ is counted among
the kinetic modes and has no precise physical interpretation. In
contrast to the previous section, here $j_\alpha(\mathbf{r};t)$
is used to represent the total flux (advective
plus diffusive) rather than the purely diffusive flux.

>>>>

A second distribution function is introduced, denoted $g_i(\mathbf{r};t)$,
which describes the composition. The moments of this distribution, by
analogy with the hydrodynamic case with distribution
$f_i(\mathbf{r};t)$ given in
Eq.~\ref{equation-lb-f-moments}, are written
\begin{equation}
\phi(\mathbf{r};t) = \sum_i g_i (\mathbf{r};t), \quad
j_\alpha(\mathbf{r};t) = \sum_i g_i(\mathbf{r};t) c_{i\alpha}, \quad
\Phi_{\alpha\beta}(\mathbf{r};t) = \sum_i g_i(\mathbf{r};t)
c_{i\alpha}c_{i\beta}.
\end{equation}
Again, the summation is over index $i$ which counts the number of
discrete velocity components for the relevant lattice Boltzmann
model $N_{\mathrm{vel}}$. However, for the Cahn-Hilliard equation,
the only relevant physical moments are the order parameter
$\phi(\mathbf{r};t)$ and the flux $j_\alpha(\mathbf{r};t)$, so
the quantity $\Phi_{\alpha\beta}(\mathbf{r};t)$ is counted among
the kinetic modes and has no precise physical interpretation. In
contrast to the previous section, here $j_\alpha(\mathbf{r};t)$
is used to represent the total flux (advective
plus diffusive) rather than the purely diffusive flux.
